Python as a machine learning language: experiences from the scikit-learn project

### 2013-06-12 paper.tex
start a future work section

\subsection{Parallelism}

@@

>>>>

\subsection{Parallelism}
\label{sec:parallel}

@@

\subsection{Future work}

The \sklearn toolkit is by no means finished,
although it is coming close to a 1.0 release.

\sklearn does not support all tasks in the broad field of machine learning,
and does not intend to either;
in particular, structured prediction and bandit-style online learning algorithms
are considered ``off-topic'' for the library,
and submissions of implementations of these for inclusion
will (at least at present) be rejected.
Collaborative filtering algorithms are not implemented
and it is remains to be seen
whether an API for them can be designed that matches the \sklearn API.

At a lower-level, a potential point of improvement
is parallel processing, which, as described in Section~\ref{sec:parallel},
is only implemented at a rather coarse-grained level.
Cython's built-in support for OpenMP \citep{dagum1998openmp}
remains a viable candidate technology
for more fine-grained multicore support in \sklearn.
